Storing messages with multipartite neural cliques

### 2014-07-22 Articles/article.tex
meilleure figure densités

	Theoretical and empirical densities match very closely, see Figure \ref{densiteth}. %gap of theoretical density with density in simulations : under $1$ percent, 
	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/remplacement_densite_c8l256a4}
		\caption{Theoretical and empirical densities for a network of 8 clusters, 256 units per cluster and 4 activated units per cluster}
			\label{densiteth}
	\end{figure}

>>>>

	Theoretical and empirical densities match very closely, see Figure \ref{densiteth}. %gap of theoretical density with density in simulations : under $1$ percent, 
	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/c5l256densities}%remplacement_densite_c8l256a4}
		\caption{Theoretical and empirical densities for networks of 5 clusters, 256 units per cluster }
			\label{densiteth}
	\end{figure}
